---
title: "Coursera Reproduciable research"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Code for reading in the dataset and/or processing the data

Import of dataset make sure that working directory is set right
```{r}
activity <- read.csv("~/activity.csv")
head(activity)
```

## 2. Histogram of the total number of steps taken each day

Aggregate function is used to calculate the daily sum of steps. NAs are removed

```{r}
sum_steps_daily <-aggregate(steps~date, activity, sum)
hist(sum_steps_daily$steps, xlab ="Classes of steps per day", ylab = "number of days", main = "Total number of steps/ day")

```

## 3. Mean and median number of steps taken each day

Use of mean and median function to calculate the values

```{r}
mean(sum_steps_daily$steps)
median(sum_steps_daily$steps)
```

## 4.Time series plot of the average number of steps taken

Use of aggregate function to create a data frame with mean steps per interval 

```{r}
mean_steps_interval<-aggregate(steps~interval , activity, mean)

with(mean_steps_interval,plot(interval,steps,type = "l"))
```

## 5. The 5-minute interval that, on average, contains the maximum number of steps

Use which.max function to determine the maxium number of steps and the report the interval using []

```{r}
mean_steps_interval[which.max(mean_steps_interval[,2]),1]
```
## 6. Code to describe and show a strategy for imputing missing data

Firstly the missing values are identified using is.na.
Then the mean of all intervals is determined.
Then all the steps which are NA are replaced with the average of all intervals. The data frame without NAs is called "activity_no_NAS"  

```{r}
missing_values<-is.na(activity$steps)

mean_of_all_intervals<-mean(mean_steps_interval$steps)

activity_no_NAS<-activity
activity_no_NAS[missing_values,1]<-mean_of_all_intervals
head(activity_no_NAS)
```

## 7. Histogram of the total number of steps taken each day after missing values are imputed

Copy paste of code for task 2 -> use data frame with no NAs

```{r}
sum_steps_daily_no_NAs <-aggregate(steps~date, activity_no_NAS, sum)
hist(sum_steps_daily_no_NAs, xlab ="Classes of steps per day", ylab = "number of days", main = "Total number of steps/ day")

```






